COCT Urban Mobility

### 2023-08-14 main_analysis.Rmd
Final analysis, main_analysis created. Draft versions archived.

x <- sort(tmp$n, decreasing = TRUE)
x <- x[6] # for top 5
sz <- 5
tmp %>% 
mutate(day_of_week = wday(creation_timestamp, label=TRUE),
       label = case_when(n > x ~ 
                           paste(day_of_week, creation_timestamp),
                         TRUE ~ ""),
       weekend = case_when(day_of_week %in% c("Sat", "Sun") ~ "weekend",
                           TRUE ~ "week")) %>%

@@

sz <- 5
 dta_dir %>% 
 mutate(day_of_week = wday(creation_timestamp, label=TRUE)) %>% 
 group_by(day_of_week, official_suburb) %>% 
 count() %>% 
   mutate(label = case_when(n >= x ~ official_suburb,
                          TRUE ~ "")) %>%
   ggplot(aes(day_of_week, n, label = label))+
   geom_jitter(alpha = 0.6, width = 0.1, colour = coct_cols[1])+
   ggrepel::geom_text_repel(alpha = 0.5, size = sz,
                            max.overlaps = 50,
                            force = 0.1)+
   labs(title = "Figure 12",
        caption = "Each dot represents a suburb, only ones with
        high numbers are labelled.")

>>>>

x <- sort(tmp$n, decreasing = TRUE)
x <- x[6] # for top 5
sz <- 7
tmp %>% 
mutate(day_of_week = wday(creation_timestamp, label=TRUE),
       label = case_when(n > x ~ 
                           paste(day_of_week, creation_timestamp),
                         TRUE ~ ""),
       weekend = case_when(day_of_week %in% c("Sat", "Sun") ~ "weekend",
                           TRUE ~ "week")) %>%

@@

sz <- 7
 dta_dir %>% 
 mutate(day_of_week = wday(creation_timestamp, label=TRUE)) %>% 
 group_by(day_of_week, official_suburb) %>% 
 count() %>% 
   mutate(label = case_when(n >= x ~ official_suburb,
                          TRUE ~ "")) %>%
   ggplot(aes(day_of_week, n, label = label))+
   geom_jitter(alpha = 0.6, width = 0.1, colour = coct_cols[1])+
   ggrepel::geom_text_repel(alpha = 0.5, size = sz,
                            max.overlaps = 50,
                            force = 0.1)+
   labs(title = "Figure 12",
        caption = "Each dot represents a suburb, only ones with
        high numbers are labelled.")
